Shades of Green

### 2023-09-26 docs/presentations/20230928-sehm_presentation.qmd
update data slide and add result section in sehm_pres

@@

@@

## Count of all SWINNO
### [5 Year MA]{.text-royal-blue-800} and [Yearly]{.text-gray-600}

plot_bioeconomy_trends_interactive(bioeconomy_share, "total_count")
```

>>>>

# Data{.inverted}
```{python}
# | label: Data
n_swinno = swinno["sinno_id"].nunique()

display(
    Markdown(
        f"""
  ## SWINNO -- A Swedish Innovation Output Database with {n_swinno} Innovations{{.smaller}}

  ### [5 Year MA]{{.text-royal-blue-800}} and [Yearly]{{.text-gray-600}}
  """
    )
)

plot_bioeconomy_trends_interactive(bioeconomy_share, "total_count")

@@

# Results{.inverted}

@@
